Centralizers of higher enveloping algebras of Lie algebras

### 2020-09-01 draft.tex
tidying up other areas

\begin{prp}\label{L:canonicaltocenterisquis} The morphism~\eqref{eq:canonicaltocenter}
\[\clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})\] is a weak-equivalence of factorization algebras. 
\end{prp}
\begin{proof}
By definition (and Lemma~\ref{L:ComTriangCent}) the map 
$\theta_f$ is a factorization algebra map between \emph{locally constant} factorization algebras. 
Therefore, in order to prove it is a weak-equivalence of factorization algebras, it is enough to prove that 
$\clies\big(\fg\otimes \Omega (U), B(U) \big) \longrightarrow  {\frak Z}(\mathbf{f})(U)$ is a quasi-isomorphism for every $U$ which is a disk, that is 
homeomorphic to $\RR^n$. This is given by lemma~\ref{L:thetaquisondisk}.
\end{proof}

\section{Factorization algebra description of the center}
\label{S:centerinFacAlg}

>>>>

\begin{prp}
\label{L:canonicaltocenterisquis} 
The map~\eqref{eq:canonicaltocenter}
\[
\clies\big(\fg\otimes \Omega , B \big) \longrightarrow  {\frak Z}(\mathbf{f})
\] 
is a quasi-isomorphism of factorization algebras. 
\end{prp}

\begin{proof}
By definition (and Lemma~\ref{L:ComTriangCent}) the map 
$\theta_f$ is a factorization algebra map between \emph{locally constant} factorization algebras. 
Therefore, in order to prove it is a weak-equivalence of factorization algebras, it is enough to prove that 
$\clies\big(\fg\otimes \Omega (U), B(U) \big) \longrightarrow  {\frak Z}(\mathbf{f})(U)$ is a quasi-isomorphism for every $U$ which is a disk, that is 
homeomorphic to $\RR^n$. This is given by lemma~\ref{L:thetaquisondisk}.
\end{proof}

\section{Functoriality of the centralizer construction}
\label{S:centerinFacAlg}

\owen{If I'm understanding, this section shows that our construction satisfies the ``composition'' of centralizers on the nose. One corollary is that the center has a strict associative product!}
